The Forensic Interchange Format - a file format for digital evidence

### 2009-02-23 paper/paper.tex
Added an initial C implementation. So far we have a mostly working Zip library.

>>>>

\subsubsection{Merging of evidence set}
In this common usage case, Bob, goes on site to image one hard disk,
while Alice independently images a second hard disk. After returning
to the office they both realise their images belong to the same
set. They merge their images, by updating the UUIDs on one of the
volume set to now belong to the other volume set - the merge is almost
instantaneous as they only need to write an extra ``properties'' file
on the merged volumes.
